An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-30 poly-embed-journal/jmlr_cover_letter/jmlr_coverletter.tex
Adding email addresses

Reviewers:
\begin{itemize}
    \item Bob Williamson, University of T\"ubingen (\url{bob.williamson@uni-tuebingen.de}
    \item Shivani Agarwal, University of Pennsylviania (\url{ashivani@seas.upenn.edu})
    \item Alex Nowak-Vila, Owkin (\url{alex.nowak-vila@inria.fr})
    \item Clayton Scott
    \item Harish Ramaswamy
      % \item Pranjal Ashwathi (see recently published ICML paper) <-- could be great, but I'd have to look into their work more; seemed more on the PAC learning side at first glance, but lots of "consistency" and "surrogates" so maybe a good fit
      % These are either too much of a stretch or too junior I think -- journal reviewers are usually more senior, though students definitely do it now and then
    % \item Yutong Wang
    % \item Han Bao, University of Tokyo / RIKEN AIP (first.lastname@institution.edu)
    % \item Authors of this paper: \url{https://arxiv.org/pdf/2202.02193.pdf} -- bit of a stretch
    % \item Satyen Kale
\end{itemize}

>>>>

Reviewers:
\begin{itemize}
    \item Bob Williamson, University of T\"ubingen (\url{bob.williamson@uni-tuebingen.de})
    \item Shivani Agarwal, University of Pennsylviania (\url{ashivani@seas.upenn.edu})
    \item Alex Nowak-Vila, Owkin (\url{alex.nowak-vila@inria.fr})
    \item Clayton Scott, University of Michigan (\url{clayscot@umich.edu})
    \item Harish Ramaswamy, IIT Madras (\url{hariguru@cse.iitm.ac.in})
      % \item Pranjal Ashwathi (see recently published ICML paper) <-- could be great, but I'd have to look into their work more; seemed more on the PAC learning side at first glance, but lots of "consistency" and "surrogates" so maybe a good fit
      % These are either too much of a stretch or too junior I think -- journal reviewers are usually more senior, though students definitely do it now and then.  FWIW, Han is junior faculty now, though agreed.
    % \item Yutong Wang
    % \item Han Bao, University of Tokyo / RIKEN AIP (first.lastname@institution.edu)
    % \item Authors of this paper: \url{https://arxiv.org/pdf/2202.02193.pdf} -- bit of a stretch
    % \item Satyen Kale
\end{itemize}
